Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-08-02 manuscript/manuscript.tex
Continue writing manuscript: added figures for exponential density

\begin{table}
\caption{Description of the synthetic grids where the comparison of the numerical model against the analytical solutions for a spherical shell was done. This collection of grids tries to include every possible scenario on which the numerical model can present a different behaviour depending on the size of the grid, its location or its height.}
\label{tab:grids}
\begin{tabular}{lcccc}
    Grid & Size & Lat. extension & Lon. extension & Height \\ \hline
    Pole & $1^\circ \times 1^\circ$ & $89^\circ - 90^\circ$ & $0^\circ - 1^\circ$ & 2km \\
    Equator & $1^\circ \times 1^\circ$ & $0^\circ - 1^\circ$ & $0^\circ - 1^\circ$ & 2km \\
    Satellite & $1^\circ \times 1^\circ$ & $89^\circ - 90^\circ$ & $0^\circ - 1^\circ$ & 260km \\
    Big Grid & $30^\circ \times 30^\circ$ & $60^\circ - 90^\circ$ & $0^\circ - 30^\circ$ & 2km \\
\end{tabular}
\end{table}

@@

\begin{equation}
    \rho(r') = 
    -\frac{3300 - 2670}{35000} r' + 
    \left( \frac{3300 - 2670}{35000} R + 2670 \right)
\end{equation}

@@

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/Dlinear-thin-differences.pdf}
\caption{}
\label{fig:D-linear-thin}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/Dlinear-thick-differences.pdf}
\caption{}
\label{fig:D-linear-thick}
\end{figure}

@@

To test the model in case of a exponential density we proposed the following function:

\begin{equation}
\rho(r') = A e^{-(r' - R)/b}
\end{equation}

\noindent where $A$ = 1 kg/m$^3$ and $b$ = 10$^6$ m.

>>>>

\begin{table}
\caption{
    Description of the synthetic grids where the comparison of the numerical model against the analytical solutions for a spherical shell was done. This collection of grids tries to include every possible scenario on which the numerical model can present a different behaviour depending on the size of the grid, its location or its height.
}
\label{tab:grids}
\begin{tabular}{lcccc}
    Grid & Size & Lat. extension & Lon. extension & Height \\ \hline
    Pole & $1^\circ \times 1^\circ$ & $89^\circ - 90^\circ$ & $0^\circ - 1^\circ$ & 2km \\
    Equator & $1^\circ \times 1^\circ$ & $0^\circ - 1^\circ$ & $0^\circ - 1^\circ$ & 2km \\
    Satellite & $1^\circ \times 1^\circ$ & $89^\circ - 90^\circ$ & $0^\circ - 1^\circ$ & 260km \\
    Big Grid & $30^\circ \times 30^\circ$ & $60^\circ - 90^\circ$ & $0^\circ - 30^\circ$ & 2km \\
\end{tabular}
\end{table}

@@

\begin{equation}
    \rho(r') = 
    -\frac{3300 - 2670}{35000} r' + 
    \left( \frac{3300 - 2670}{35000} R + 2670 \right)
    \label{eq:density-linear}
\end{equation}

@@

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/Dlinear-thin-differences.pdf}
\caption{
    Differences between the gravity fields generated by the numerical model and the analytical solution for a thin spherical shell of 1km of thickness and the linear density defined on equation \ref{eq:density-linear}. The computations were performed on the four grids described in Table \ref{tab:grids} and for different values of the distance-size ratio $D$. If the difference is less than 10$^{-1}\%$, we consider that the model has achieved an acceptable accuracy for the corresponding value of $D$.
}
\label{fig:D-linear-thin}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/Dlinear-thick-differences.pdf}
\caption{
    Differences between the gravity fields generated by the numerical model and the analytical solution for a thick spherical shell of 35km of thickness and the linear density defined on equation \ref{eq:density-linear}. The computations were performed on the four grids described in Table \ref{tab:grids} and for different values of the distance-size ratio $D$. If the difference is less than 10$^{-1}\%$, we consider that the model has achieved an acceptable accuracy for the corresponding value of $D$.
}
\label{fig:D-linear-thick}
\end{figure}

@@

To test the model in case of an exponential density we proposed the following function:

\begin{equation}
    \rho(r') = A e^{-(r' - R)/b}
\label{eq:density-exp}
\end{equation}

\noindent where $A$ = 1 kg/m$^3$ and $b$ = 10$^6$ m.
We have also performed this test with a thin and a thick shell of 1 km and 35 km, respectively.
The results can be seen in Figures \ref{fig:D-exp-thin} and \ref{fig:D-exp-thick}.

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/Dexp-shifted-thin-differences.pdf}
\caption{
    Differences between the gravity fields generated by the numerical model and the analytical solution for a thin spherical shell of 1km of thickness and the exponential density defined on equation \ref{eq:density-exp}. The computations were performed on the four grids described in Table \ref{tab:grids} and for different values of the distance-size ratio $D$. If the difference is less than 10$^{-1}\%$, we consider that the model has achieved an acceptable accuracy for the corresponding value of $D$.
}
\label{fig:D-exp-thin}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/Dexp-shifted-thick-differences.pdf}
\caption{
    Differences between the gravity fields generated by the numerical model and the analytical solution for a thick spherical shell of 35km of thickness and the exponential density defined on equation \ref{eq:density-exp}. The computations were performed on the four grids described in Table \ref{tab:grids} and for different values of the distance-size ratio $D$. If the difference is less than 10$^{-1}\%$, we consider that the model has achieved an acceptable accuracy for the corresponding value of $D$.
}
\label{fig:D-exp-thick}
\end{figure}
